A free/open-source machine translation system for English to Kazakh

### 2015-03-07 engkaz-eamt-2015/engkaz-eamt-2015.tex
remove comments
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59256 72bbbca6-d526-0410-a7d9-f06f51895060
caught a minor mistake
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@59257 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{abstract}
This paper presents the current state of development a shallow-transfer rule-based machine 
translation (MT) system from English to Kazakh. The main syntactic and morphological differences 
between the two languages are presented, and it is showed how the MT 
system was designed to tackle these challenges. We show an evaluation of system coverage and 
translation quality and outline and future work.
\end{abstract}

@@

  there are three possible outcomes with different cases:\todo{remove braces for consistency with the previous notation for archiphonemes: avoid repeating the explanation in the footnote.}

@@

\todo{Some references didn't come out right.} 
\bibliographystyle{apalike}

>>>>

\begin{abstract}
This paper presents the current state of development a shallow-transfer rule-based machine 
translation (MT) system from English to Kazakh. The main syntactic and morphological differences 
between the two languages are presented, and it is shown how the MT 
system was designed to tackle these challenges. We show an evaluation of system coverage and 
translation quality and outline and future work.
\end{abstract}

@@

  there are three possible outcomes with different cases:

@@

%\todo{Some references didn't come out right.} 
\bibliographystyle{apalike}
